Clustering of Last.fm Music

### 2015-05-07 writeup/MSDgroupwriteup.tex
Update MSDgroupwriteup.tex

\subsection{User Based and Item Based Collaborative Filtering}
%\subsubsection{Intro to Memory-Based Collaborative Filtering}
A simpler set of methods for determining which songs to recommend to individual users is by using user- or item/song- based similarity (both also considered collaborative filtering). These only consider whether or not a user listened to a song and does not take into account the play count. Similarity scores between users (i.e. user-based) and songs (i.e. item-based) were calculated using cosine similarity. Intuitively, they work by recommending users songs that other similar users like (user-based) or by recommending songs which are similar to the songs the user has already listened to (item-based).

>>>>

\subsection{User Based and Item Based Collaborative Filtering}
%\subsubsection{Intro to Memory-Based Collaborative Filtering}
A simpler set of methods for determining which songs to recommend to individual users is by using user- or item/song- based similarity (both also considered collaborative filtering). These only consider whether or not a user listened to a song and does not take into account the play count. Similarity scores between users (i.e. user-based) and songs (i.e. item-based) were calculated using cosine similarity. Intuitively, they work by recommending users songs that other similar users like (user-based) or by recommending songs which are similar to the songs the user has already listened to (item-based). The downside to this method is the computational complexity. Given the quadratic runtime of these algorithms, they are more difficult to scale to a larger dataset. As for storage requirements, we will have to store all pairs of similarity scores for users in the case of user-based and songs in the case of item-based. The details are described below.
